### 2021-06-17 paper/model/estimated_parameters.tex
Put estimated infection probabilities into a table.

@@

To calibrate infection probabilities outside of the model, it would be important to know
the exact duration and distance of each contact type as well as viral loads. Since this
is not available in any data set, we estimate those parameters inside the model with the
method of simulated moments \citep{McFadden1989} by minimizing the distance between
simulated and observed infection rates. Since our model includes a lot of randomness, we
average simulated infection rates over several model runs.

@@

The infection probabilities estimated from our model are as follows: For household
contacts (each individual meets all his or her household members every day) the infection
probability is 10\%, for school contacts (all students and teachers meet all other
students and teachers that attend school that day and there are three classes taking
place each day) the probability of infection is 1.2\%, for preschools and nurseries that
infection probability is 0.5\%. Work contacts carry a risk of 14.5\% and other activities
(including leisure activities such as meeting friends) carry the highest risk with
15.875\%.\comment[id=HM]{Are these numbers current? In any case, a table would substitute for this and the previous paragraph. Need to mention B.1.1.7 alongside.}\comment[id=K]{Missing to add data for the other estimated parameters (import of b117 etc)}

>>>>

We estimate parameters that could not be calibrated inside the model with the
method of simulated moments \citep{McFadden1989} by minimizing the distance between
simulated and observed infection rates. Since our model includes a lot of randomness, we
average simulated infection rates over several model runs.

@@

@@

The infection probabilities estimated from our model are as shown in
Table~\ref{tab:infection_probs}.\comment[id=K]{Missing to add data for the other
estimated parameters (import of b117 etc)}\comment[id=K]{Update table after the new
estimation is finished}

\begin{table}[tb]
    \caption{Estimated Infection Probabilities}
    \label{tab:infection_probs}
    \centering
    \begin{tabular}{ll}
        \toprule
        Contact Type & Infection Probability \\
        \midrule
        preschool and nursery & 00.500\% \\
        school & 01.200\% \\
        household & 10.000\% \\
        work & 14.500\% \\
        other & 15.875\% \\
        \bottomrule
    \end{tabular}
    \tablenotes{School contacts take place Monday through Friday. All students and
teachers meet all other students and teachers that attend school that day and there are
three classes taking place each day. Work contacts can be daily, weekly or non recurrent.
Other contacts can be daily, weekly or non recurrent. We do not differ the infection
probability depending on how often a contact takes place.}
\end{table}
